Critical Temperature of Superconductors YBCO and BSCCO

### 2014-11-20 Draft.tex
intro

\section{Introduction} % Section titles are automatically converted to all-caps.
% Section numbering is automatic.
In 1911, Kamerlingh Onnes discovered superconductivity in mercury.  
Instead of a gradual decrease in the electrical resistance as the temperature decreased, he found a sudden loss of resistance when the temperature went below 4.2 K. 
The temperature at which the resistance disappears is called the critical temperature.
In addition to having no resistance, superconductors also exhibit perfect diamagnetism, so it excludes magnetic field flux. 
This property, called the Meissner effect, was found in 1933.

@@

>>>>

\section{Introduction} % Section titles are automatically converted to all-caps.
% Section numbering is automatic.
In 1911, Kamerlingh Onnes discovered superconductivity in mercury.  
Instead of a gradual decrease in the electrical resistance as the temperature decreased, he found a sudden loss of resistance when the temperature went below 4.2 K. 
The temperature at which the resistance disappears is called the critical temperature.
In addition to having no resistance, superconductors also exhibit perfect diamagnetism, which means they exclude all magnetic field flux from their interior. 
This property, called the Meissner effect, was discovered in 1933.\cite{intro}
A common demonstration of the Meissner effect is to place a a magnet on top of a superconductor above its critical temperature. When the superconductor is cooled to become superconducting, the magnet will start to levitate above the superconductor. 
This phenomenon can be used to make levitation trains.  Superconductors are also used to create magnetic fields used in magnetic resonance imaging and in high energy physics to accelerate and control the path of particles.\cite{kumar}

Superconductivity has been found to occur in elements, alloys, binary compounds, and other materials.  
Roughly 70 years after superconductivity was discovered, ceramic materials with critical temperatures above the liquid nitrogen temperature of 77 K were found.\cite{melissinos} 
These ``high temperature'' superconductors were made up of alternating layers of rare earth atoms and copper and oxygen atoms.\cite{kumar} In our experiment, we look at two high temperature superconductors, $\textrm{Yt}_{?}\textrm{Ba}_{?}\textrm{Cu}_{?}\textrm{O}_{?}$ and $\textrm{Bi}_{?}\textrm{Sr}_{?}\textrm{Ca}_{?}\textrm{Cu}_{?}\textrm{O}_{?}$.

@@

\bibitem{intro} Charles Poole, Horacio Farach, and Richard Creswick, \textit{Superconductivity} (Academic Press, 2007).

\bibitem{kumar} Ajay Kumar Saxena, \textit{High-Temperature Superconductors} (Springer Berlin Heidelberg, 2010).

\bibitem{melissinos} Experiments in Modern Physics.  Adrian Constantin Melissinos and Jim Napolitano.  Gulf Professional Publishing, 2003
